Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-03-13 docs/thesis/chap-future_work.tex
proofreading fixes
minor fixes to the document: distributed system(s) latex_editor (that)

\section{Data Analysis}
Different algorithms and techniques have been developed to overcome some of the shortcomings of the vector space model. Latent semantic indexing together with singular value decomposition, allow to automatically identify synonyms which can improve the recall of an IR system. During our work, we tested different projects such as Semantic Vectors\cite{semantic_vectors} and \cite{mallet} and Mahout. However, these tools are not yet ready for a big deployment and a considerable amount of time and effort was spent on trying to integrate the formats from the Lucene index to the input format of each tool, as well as debugging and fixing code of some of the tools to make them work. Several times we encountered errors due to the in-memory implementations of the algorithms. Further work on integrating the results of these techniques to the workflow of the system could provide better results.

@@

\section{End to end system}
In our implementation, we explored and incorporated \LaTeX extraction to our system. For a full integration on CDS, PDF extraction becomes an important need since most of the records that do not include the source files.

>>>>

\section{Data Analysis}
Different algorithms and techniques have been developed to overcome some of the shortcomings of the vector space model. Latent semantic indexing together with singular value decomposition, allow to automatically identify synonyms which can improve the recall of an IR system. During our work, we tested different projects such as Semantic Vectors\cite{semantic_vectors} and Mallet\cite{mallet} and Mahout. However, these tools are not yet ready for a big deployment and a considerable amount of time and effort was spent on trying to integrate the formats from the Lucene index to the input format of each tool, as well as debugging and fixing code of some of the tools to make them work. Several times we encountered errors due to the in-memory implementations of the algorithms. Further work on integrating the results of these techniques to the workflow of the system could provide better results.

@@

\section{End to end system}
In our implementation, we explored and incorporated \LaTeX extraction to our system. For a full integration on CDS, PDF extraction becomes an important need since most of the records do not include the source files.
